---
output: rmarkdown::github_document
---

# rrecog

Pattern Recognition for Hosts, Services and Content

## Description

'Rapid7' developed a framework dubbed 'Recog' <https://github.com/rapid7/recog> to facilitate fingerprinting hosts, services and content. The original program was written in 'Ruby'. Tools are provided to download and match fingerprints using R.
    
## What's Inside The Tin

The following functions are implemented:

- `download_fingerprints`:	Download fingerprints from the Recog repo
- `load_fingerprints`:	Load a directory of fingerprints
- `read_fingerprints_file`:	Ingest Recog XML fingerprints from a file and precompile regular expressions
- `recog_match`:	Find fingerprint matches for a given source
- `use_builtin_fingerprints`:	Use built-in fingerprints

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/rrecog")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rrecog)

# current verison
packageVersion("rrecog")

```

### Use Real Data

```{r}
library(httr)
library(tidyverse)

# using the internet as a data source is fraught with peril
safe_GET <- safely(httr::GET)

sprintf(
  fmt = "http://%s", 
  c(
    "r-project.org", "pypi.org", "www.mvnrepository.com", "spark.apache.org",
    "www.oracle.com", "www.microsoft.com", "www.apple.com", "feedly.com"
  )
) -> use_these

pb <- progress_estimated(length(use_these))
map(use_these, ~{
  pb$tick()$print()
  res <- safe_GET(.x, httr::timeout(2))
  if (is.null(res$result)) return(NULL)
  res$result$headers$server
}) %>% 
  compact() %>% 
  flatten_chr() -> server_headers

server_headers

recog_db <- use_builtin_fingerprints()
map_df(server_headers, ~recog_match(recog_db, .x, "http")) %>%
  glimpse() -> found

select(found, orig, service.vendor, service.version, apache.info, description)
```
